### 2020-10-20 thesis/chap_1.tex
adress comment 12
adress comment 29
comment 50

The ST-Sim model uses three states: Forest, Urban and Agriculture. Forest was further subdivided into classes of age and type, derived from the LANDIS outputs: three forest types (\textbf{deciduous}, \textbf{mixt}, and \textbf{coniferous}) and three age classes (\textbf{young}, \textbf{medium}, and \textbf{old}) for a total of 9 classes.
The model allows for 4 groups of transitions:
\begin{itemize}
\item{\textbf{Urbanisation}}: groups \textbf{deforestation} (Forest $\Rightarrow$ Urban) and \textbf{agricultural loss} (Agriculture $\Rightarrow$ Urban).
\item{\textbf{Agricultural expansion}} (Forest $\Rightarrow$ Urban).
\item{\textbf{Forest Internals}}: groups the 72 combinations of forest change between the 9 forest internal states.
\end{itemize}
The model takes in 3 different strata. A stratum in ST-Sim refers to a subset of the entire landscape being considered for analysis. Strata are typically used to divide the overall landscape into regions or zones, each of which can have different model parameters specified. The three stratum are:
\begin{itemize}
\item{Primary stratum:} delineates Montérégie from the  surrounding buffer and highlights protected areas.
\item{Secondary stratum:} delineates municipalities of the region, to allow to set targets specific to each municipality.
\item{Tertiary stratum:} delineates LANDIS land types, to allow to set transition multipliers for forest types that match the LANDIS simulations. \\
\end{itemize}

@@

\subparagraph*{\textit{Current flow}} We see a clear difference in changes to current flow between the two scenarios (BAU and Reforestation, with a significant difference in the slopes of the two scenarios, independent of the species considered (see figure \ref{fig:flow_linear_1} for a linear graph and \ref{fig:flow_linear_1} for a radar representation). Although both scenarios still predict a trend of decreasing mean flow, not all species react to the same degree. Only the black bear (\textit{Ursus americanus}) - and, to a lesser extent, the short-tailed shrew (\textit{Blarina brevicauda}) - manage to maintain a similar level of mean flow under the Reforestation scenario.

@@

% Review results and contrast with other papers integrating LUC and CC models
Other studies have attempted to go beyond those issues and managed to integrate climate and land use change models to some degree. For example, \cite{albert_applying_2017}, on which this work is based, assessed whether certain habitat networks in the Montérégie would be more resilient to future change using several multi scale metrics of connectivity. \cite{leonard_landscape-scale_2017} used systematic conservation planning methods to identify core areas and linkages under an energy development land use change scenario in the northeastern US. In another study, \cite{dilts_multiscale_2016} used a range of graph theoretic metrics to forecast the changes to diverse aspects of habitat connectivity for the Mohave ground squirrel under multiple climate and land use change scenarios. Although our results, contrary to those studies, do not allow us to derive prescriptive network design for our study species, they do offer valuable insights for the design of such networks in the future.

>>>>

The ST-Sim model uses three states: Forest, Urban and Agriculture. Forest was further subdivided into classes of age and type, derived from the LANDIS outputs: three forest types (\textbf{deciduous}, \textbf{mixt}, and \textbf{coniferous}) and three age classes (\textbf{young}, \textbf{medium}, and \textbf{old}) for a total of 9 classes.
The model allows for 4 groups of transitions:
\begin{itemize}
\item{\textbf{Urbanisation}}: groups \textbf{deforestation} (Forest $\Rightarrow$ Urban) and \textbf{agricultural loss} (Agriculture $\Rightarrow$ Urban).
\item{\textbf{Agricultural expansion}} (Forest $\Rightarrow$ Agriculture).
\item{\textbf{Forest Internals}}: groups the 72 combinations of forest change between the 9 forest internal states.
\end{itemize}
The model takes in 3 different strata. A stratum in ST-Sim refers to a subset of the entire landscape being considered for analysis. Strata are typically used to divide the overall landscape into regions or zones, each of which can have different model parameters specified. The three stratum are:
\begin{itemize}
\item{Primary stratum:} delineates Montérégie from the  surrounding buffer and highlights protected areas.
\item{Secondary stratum:} delineates municipalities of the region, to allow to set targets specific to each municipality.
\item{Tertiary stratum:} delineates LANDIS land types, to allow to set transition multipliers for forest types that match the LANDIS simulations. \\
\end{itemize}

@@

\subparagraph*{\textit{Current flow}} We see a clear difference in changes to current flow between the two scenarios (BAU and Reforestation, with a significant difference in the slopes of the two scenarios, independent of the species considered (see figure \ref{fig:flow_linear_1} for a linear graph and \ref{fig:flow_radar_1} for a radar representation). Although both scenarios still predict a trend of decreasing mean flow, not all species react to the same degree. Only the black bear (\textit{Ursus americanus}) - and, to a lesser extent, the short-tailed shrew (\textit{Blarina brevicauda}) - manage to maintain a similar level of mean flow under the Reforestation scenario.

@@

% Review results and contrast with other papers integrating LULCC and CC models
Other studies have attempted to go beyond those issues and managed to integrate climate and land use change models to some degree. For example, \cite{albert_applying_2017}, on which this work is based, assessed whether certain habitat networks in the Montérégie would be more resilient to future change using several multi scale metrics of connectivity. \cite{leonard_landscape-scale_2017} used systematic conservation planning methods to identify core areas and linkages under an energy development land use change scenario in the northeastern US. In another study, \cite{dilts_multiscale_2016} used a range of graph theoretic metrics to forecast the changes to diverse aspects of habitat connectivity for the Mohave ground squirrel under multiple climate and land use change scenarios. Although our results, contrary to those studies, do not allow us to derive prescriptive network design for our study species, they do offer valuable insights for the design of such networks in the future.
